---
title: "enrichMiR Benchmark SFig 4 - sets and background"
author: "Pierre-Luc Germain"
date: "2021/02/13"
output: html_document
---


```{r, include=FALSE}
if(!exists('FIG_NB')){
  FIG_NB <- 0; FIG_STRING <- "Supplementary Figure S"
  getFigNb <- function(increment=FALSE){
    if(increment) FIG_NB <<- FIG_NB + 1
    paste0(FIG_STRING,FIG_NB)
  }
}
```

# `r getFigNb(TRUE)`

```{r}
suppressPackageStartupMessages({
library(cowplot)
library(ggrepel)
library(ComplexHeatmap)
library(grid)
library(scales)
library(ggthemes)
})
source("../../Benchmark/functions.R")
```


```{r}
n <- 3
col_vector = tableau_color_pal('Tableau 10')(n)
```


```{r, fig.height=8, fig.width=7, message=FALSE, warning=FALSE}
e <- readRDS("../../Benchmark/Benchmark_ms/sets2/aggregated.rds")
dss <- c(ratPolyA="rat", "amin"="Amin et al.", "bartel.hek"="HEK", "bartel.hela"="HeLa")
e <- e[which(e$method!="ebayes"),]
ag <- aggregate(e[,grep("^FP|^TP|FDR",colnames(e))], 
                by=e[,c("dataset","method","annotation")], FUN=mean)
ag$dataset <- dss[as.character(ag$dataset)]
ag$annotation <- gsub(" ","\n",ag$annotation)
ag <- ag[ag$method != "regmir.cc",]

p2 <- ggplot(ag, aes(FDR, TP.atFDR05, colour=method, label=method)) + 
  geom_point(size = 1.5) + ggrepel::geom_text_repel() + theme_bw() + 
  facet_grid(annotation~dataset) + scale_x_continuous(breaks=pretty_breaks(4)) + 
  scale_y_continuous(breaks=pretty_breaks(4)) + theme(legend.position="none") +
  labs(y="Sensitivity (TPR)", x="False Discovery Rate (FDR)", 
       title="Comparison across annotations") + scale_color_manual(values = col_vector)  +
  theme(
      strip.text.x = element_text(size = 11, color = "white"),strip.background = element_rect(color="black", fill="black"),
      strip.text.y = element_text(size = 11, color = "white"))

p2
```


### `r getFigNb()`

**Benchmark performance of the statistical tests using different target annotations.** Applicability of the top tests to scanMiR-based annotations, and comparison of the two annotations. Of note, the best tests using the conserved TargetScan annotation perform poorly with larger target annotations; for scanMiR annotations we recommend the lmadd test.
