---
title: "enrichMiR_Kleaveland_2018"
author: "Michael Soutschek"
date: "31 1 2021"
output: html_document
---

```{r, include=FALSE}
if(!exists('FIG_NB')){
  FIG_NB <- 0; FIG_STRING <- "Supplementary Figure S"
  getFigNb <- function(increment=FALSE){
    if(increment) FIG_NB <<- FIG_NB + 1
    paste0(FIG_STRING,FIG_NB)
  }
}
knitr::opts_chunk$set(fig.width=8)
```

# `r getFigNb(TRUE)`

```{r, message=FALSE,warning=FALSE}
suppressPackageStartupMessages({
library(SummarizedExperiment)
devtools::load_all("/mnt/schratt/enrichMiR/")
library(ggrepel)
library(data.table)
library(cowplot)
})
```


```{r}
#sets
sets_TS <- readRDS("/mnt/schratt/enrichMiR_data/Targetscan/20211124_Targetscan8_Mouse_ConPred_mouse.rds")

#dea
ls <- list.files("../../enrichMiR_Seq_datasets/Kleaveland_2018/data/",full.names = TRUE)
names_vec <- list.files("../../enrichMiR_Seq_datasets/Kleaveland_2018/data/")
names_vec <- sapply(strsplit(names_vec,"_"),"[",3)
names_vec <- gsub("\\.txt.gz","",names_vec)
names_ed <- c("Brain - Anterior cortex", "Brown adipose tissue","Brain - Cerebellum","Brain - Cortex","Brain - Hippocampus","Pancreatic islets","Pituitary","Skeletal muscle","Spleen","Brain - Striatum/Thalamus")

#miRNA expression

##Brain
miRBrain <-  getMouseMirExp("Brain")
miRBrain <- matchMirExpr(me = miRBrain,setsNames = sets_TS)

##Pancreas
miRPancreas <-  getMouseMirExp("Pancreas")
miRPancreas <- matchMirExpr(me = miRPancreas,setsNames = sets_TS)

##Muscle
miRMuscle <-  getMouseMirExp("Muscle")
miRMuscle <- matchMirExpr(me = miRMuscle,setsNames = sets_TS)

##Spleen
miRSpleen <-  getMouseMirExp("Spleen")
miRSpleen <- matchMirExpr(me = miRSpleen,setsNames = sets_TS)

```


```{r}
#set parameters
enr.field = "enrichment"
sig.field = "FDR"
col.field =  "expression"
label.enr.thres = 0.25
label.sig.thres=0.25
max.sig.thres=100
opacity=0.75
maxLabels = 10
label.field = "members"
size.field = "overlap"
min.enr.thres=0
```




```{r,message=FALSE,warning=FALSE}
#create the list
enr_list <- list()
for(i in 1:10){
  #load data
  dea <- fread(ls[i])
  colnames(dea)[which(colnames(dea)=="log2(CyrKO/CyrWT)")] <- "logFC"
  dea <- dea[dea$baseMean > 10,]
  props <- NULL
  if(grepl("Brain",names_ed[i])) props <- miRBrain
  if(grepl("Pancreatic",names_ed[i])) props <- miRPancreas
  if(grepl("muscle",names_ed[i])) props <- miRMuscle
  if(grepl("Spleen",names_ed[i])) props <- miRSpleen
  
  #enrichMiR
  enr <- testEnrichment(dea,sets = sets_TS,tests = "siteoverlap", sets.properties = props)
  res <- getResults(enr,test = c("siteoverlap.down"),flatten = TRUE)
  
  #plot
  if(is.null(label.field)){
      res$set <- row.names(res)
      label.field <- "set"
    }else{
      if(length(label.field<- head(intersect(label.field,colnames(res)),n=1))==0)
        stop("`label.field` not found.")
    }
  if(!is.null(min.enr.thres)) res <- res[res[[enr.field]]>=min.enr.thres,]
  res[["overlap"]] <- as.numeric(res[["overlap"]])
  res[["set_size"]] <- as.numeric(res[["set_size"]])
  res <- res[order(res[[sig.field]]),]
  res <- res[which(res[[sig.field]] <= max.sig.thres),]
  w <- which(abs(res[[enr.field]])>=label.enr.thres & 
                 res[[sig.field]]<label.sig.thres)
  w <- head(w,n=maxLabels)
  sig.field2 <- paste0("-log10(",sig.field,")")
  res[[sig.field2]] <- -log10(res[[sig.field]])
  ll <- list(label=label.field, x=enr.field, y=sig.field2)
  if(!is.null(size.field)) ll$size <- size.field
  if(!is.null(props)) ll$colour <- col.field
  for(f in setdiff(colnames(res), unlist(ll))) ll[[f]] <- f
  
  p <- ggplot(res, do.call(aes_string, ll)) + geom_point(alpha=opacity) + 
    geom_text_repel(data=res[w,],show.legend = FALSE, point.padding = 3,size = 3) + theme_classic() + 
    ggtitle(names_ed[i]) + ylim(0,5.5)
  if(!is.null(props)) p <- p + scale_colour_viridis_c(direction = -1) + labs(colour="expression") + guides(overlap = guide_legend(order = 2),colour = guide_colorbar(order = 1))
  
  #add to list
  enr_list[[names_ed[i]]] <- p
}
```



```{r,fig.width=12, fig.height=12.5}
pp <- plot_grid(plotlist = enr_list,labels = "AUTO",ncol = 3)
pp
#ggsave("Suppl_3.png",plot = pp,units = "in",width = 12,height = 14,bg = "white")
```

### `r getFigNb()`

**enrichMiR analyses on RNA-sequencing datasets generated from several mouse tissues upon Cyrano knockout. A-J** Enrichment plots on the individual DEAs with genes expressed higher than a baseMean of 10. Bubbles correspond to miRNA families including a colour coded expression of its top expressed member where applicable. miRNA expresion values were applied using the preset mouse miRNA expression tables provided in enrichMiR with the following specifications: **(A,D-E,J)** "Brain", **(F)** "Pancreas", **(H)** "Muscle" & **(I)** "Spleen".


