---
title: "enrichMiR Benchmark SFig 4 - sets and background"
author: "Pierre-Luc Germain"
date: "2021/02/13"
output: html_document
---


```{r, include=FALSE}
if(!exists('FIG_NB')){
  FIG_NB <- 0; FIG_STRING <- "Supplementary Figure S"
  getFigNb <- function(increment=FALSE){
    if(increment) FIG_NB <<- FIG_NB + 1
    paste0(FIG_STRING,FIG_NB)
  }
}
```

# `r getFigNb(TRUE)`

```{r}
suppressPackageStartupMessages({
library(cowplot)
library(ggrepel)
library(ComplexHeatmap)
library(grid)
library(scales)
library(RColorBrewer)
library(ggthemes)
})
source("../../Benchmark/functions.R")
```

```{r}
n <- 4
col_vector = tableau_color_pal('Tableau 10')(n)
```



```{r, fig.height=9, fig.width=7, message=FALSE, warning=FALSE}
e <- readRDS("../../Benchmark/Benchmark_ms/back/aggregated.rds")
dss <- c(ratPolyA="rat", "amin"="Amin et al.", "bartel.hek"="HEK", "bartel.hela"="HeLa")
ag <- aggregate(e[,grep("^FP|^TP|FDR",colnames(e))], 
                by=e[,c("dataset","method","background")], FUN=mean)
ag$dataset <- dss[as.character(ag$dataset)]
p1 <- ggplot(ag, aes(FDR, TP.atFDR05, shape=background, label=background)) + 
  geom_point(size = 2) + ggrepel::geom_text_repel() + facet_grid(~dataset) +
  theme_bw() + theme(legend.position="none") + labs(y="Sensitivity") +
  ggtitle("Using a specific background") +
  theme(
      strip.text.x = element_text(size = 11, color = "white"),strip.background = element_rect(color="black", fill="black"))

e <- readRDS(file="../../Benchmark/Benchmark_top5000/aggregated.rds")
e <- e[which(e$method!="ebayes"),]
e <- e[which(e$method!="gsea"),]
h1 <- bmhm(e, doSort=TRUE)
h2 <- bmhm(e, value.var="FDR", doSort=TRUE)

ag <- aggregate(e[,grep("^FP|^TP|FDR",colnames(e))], 
                by=e[,c("dataset","method")], FUN=mean)
p <- ggplot(ag, aes(FDR, TP.atFDR05, colour=method, label=method)) + geom_point() + 
  ggrepel::geom_text_repel(data=ag[ag$method %in% c("areamir","woverlap","siteoverlap","lmadd"),], show.legend = FALSE) + 
  facet_wrap(~dataset) + theme_bw() + scale_color_manual(values =  col_vector) +
  theme(
      strip.text.x = element_text(size = 11, color = "white"),strip.background = element_rect(color="black", fill="black"), 
      legend.position = "none")

pp1 <- cowplot::plot_grid(
    grid.grabExpr(draw(h1)), 
    grid.grabExpr(draw(h2)), nrow=1)
title <- ggdraw() + draw_label("Restricting to top 5'000 expressed genes",x = 0, hjust = 0) + theme(plot.margin = margin(0, 0, 0, 40))
p2 <- cowplot::plot_grid(title,pp1,
  p, nrow=3, rel_heights = c(0.1,1,1))



plot_grid(p1, NULL, p2, nrow=3, labels=c("A","","B"), rel_heights=c(1,0.1,2.2), scale=c(0.93,0.95))
```


### `r getFigNb()`

**Benchmark performance of the statistical tests without appropriate background specification as well as with using only the top 5'000 expressed genes. A:** Impact of using a background (TRUE), i.e. the set of expressed genes, or all genes (FALSE) on the accuracy and FDR of the prediction when using set-based analysis (based on the siteoverlap test).
**B:** Using the top performing tests on only the 5'000 highest expressed genes in the benchmarking datasets. As expected, due to a lower number of potentially annotated targets the sensitivity of most tests decreases. However, the relative performance of some of the tests changes (with e.g. the woverlap test being particularly more powerful).
